\documentclass[manuscript,screen]{acmart}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\settopmatter{printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

\begin{document}

\title{Cover Letter}
\authorsaddresses{}

\maketitle

\noindent{Dear Editor-in-Chief and Associate Editor,}

\vspace{0.5cm}

\noindent{Thank you for inviting us to submit our work for publication in TODS as one of the``best of SIGMOD 2023'' papers. This manuscript is an updated version of our SIGMOD 2023 paper, GoodCore: Data-effective and Data-efficient Machine Learning through Coreset Selection over Incomplete Data. We believe that the updated version will bring valuable insights to the database community and be a valuable addition to TODS.
The authors of this manuscript are Chengliang Chai (Beijing Institute of Technology, China), Kaisen Jin (Beijing Institute of Technology, China), Nan Tang (HKUST GZ, China), Ju Fan (Renmin University, China), Dongjing Miao (Harbin Institute of Technology, China), Yuyu Luo (HKUST GZ, China), Jiayi Wang (Tsinghua University, China), Guoliang Li (Tsinghua University, China), Ye Yuan (Beijing Institute of Technology, China), Guoren Wang (Beijing Institute of Technology, China). We confirm that this manuscript %does not overlap with any paper by any author other than the SIGMOD 2023 paper, nor does it include any anonymous citation. 
	does not include any anonymous citation. Potential conflicts of interest are listed below.

$\bullet$  Known family relationship asspouse, child, sibling, orparent: None.

$\bullet$  Business or professional partnership: None.

$\bullet$  Past or presentassociation as thesis advisoror thesis student: Guoliang Li (Tsinghua University)

$\bullet$  Collaboration on a projector on a book, article, report, or paper with in the last 48 months: Lei Cao (MIT)

$\bullet$  Co-editing of a journal, compendium, or conference proceedings within the last 24 months: None.

$\bullet$  Other relationship: None.

\vspace{0.5cm}

\noindent{Best regards,}

\noindent{Chengliang Chai}

\noindent{Beijing Institute of Technology}

\end{document}


